Flute and kink instabilities in a dynamically twisted flux tube with anisotropic plasma viscosity

### 2021-12-27 paper.tex
Add paragraph in introduction motivating changing resistivity

>>>>

\rev{It will be shown in our results that the flute instability is driven by
a pressure gradient generated through Ohmic heating, so the value of
resistivity is an important parameter in the development of the instability. In
addition to exploring the effect of viscosity model on the flute instability,
we also explore the effect of varying resistivity. Ideally, our simulations
would be performed using a realistic coronal resistivity of approximately
$10^{-8}$~\citep{craigAnisotropicViscousDissipation2009a} however due to the
dissipative nature of numerical schemes (particularly when using shock
capturing techniques) this is computationally infeasible. In order to provide
some sense of the scaling expected with resistivity, to allow us to speculate
about the expected results at coronal values, we perform our simulations at
two, computationally accessible values of resistivity, $10^{-3}$ and $10^{-4}$.
This is not intended to replace a full parameter study so we will speculate
whether our results generalise to lower values of resistivity but will not
attempt to quantify any scaling laws or suggest concrete trends.}
